---
title: "AAVSO-Zapper Summulator"
author: "David J Jackson"
date: "2/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(plotly)

```
```{r Import Data,echo=FALSE}
rm(list=ls())
alf_ori <- fread("../db/Alf_Ori-corrected.csv")
# alf_ori <- fread(file.choose())
alf_ori$Ymd <- as.Date(paste(alf_ori$year, alf_ori$month, alf_ori$day, sep = "-"))
alf_ori <- janitor::clean_names(alf_ori)
alf_ori <- alf_ori %>% select(ymd,year,month,vis) 

```




### The Whole Enchilada: Jan - 1918 to Feb. 2020
```{r, echo=FALSE}
plot_ly(alf_ori) %>% add_lines(x=~ymd,y=~vis) %>%
  layout(yaxis=list(autorange="reversed"))
```
```{r}
summary(alf_ori)
```


### AAVSO Zapper Simulator (DataVerificaton)

Positive observations more than 1 magnitude brighter or fainter than the mean magnitude.

Make sure you are comparing observations made using the same color filter with each other (don't try to compare a CCDB observation with a visual one, for instance). 

Also,make sure you are comparing observations made at approximately the same time (for some stars, significant changes in behavior can occur in a very short time.)

  *  Fainter-than observations that are fainter than t5>he mean curve.
  *  Observations made during the "seasonal gap" of a star.
  *  For novae and supernovae, positive observations made before outburst.


```{r,echo=FALSE}
box_plot <-alf_ori %>% filter(ymd >="2020-01-01") 
plot_ly(box_plot) %>% add_boxplot(x = ~ymd, y = ~vis) %>%
  layout(yaxis=list(autorange="reversed"))


```
```{r}
box_plot_stats <- alf_ori %>% filter(ymd >="2000-01-01") %>%
  group_by(ymd) %>% 
  summarize(mean=mean(vis),
            max=mean+1, min=mean-1)
gg <- ggplot(box_plot_stats, aes(ymd, mean, ymin=min, ymax=max)) +
  geom_pointrange() 



```