---
title: "AAVSO Zapper Summulator"
subtitle: "JUlian Dates"
author: "David J Jackson"
date: "2/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(plotly)
library(insol)


```
```{r Import Data,echo=FALSE}
rm(list=ls())
betelguese <- fread("../db/and_aq.csv")
betelguese$JD <- as.character(betelguese$JD)
betelguese$JDate <- as.integer(betelguese$JD)
betelguese <- janitor::clean_names(betelguese)
betelguese$Ymd <- JD(betelguese$j_date,inverse = TRUE)
# betelguese$Ymd <- as.Date(betelguese$Ymd)
betelguese$Ymd <- as.Date(betelguese$Ymd)
# betelguese$jd <- as.character(betelguese$jd)
##
betelguese$band <- as.factor(betelguese$band)
betelguese$magnitude <- as.numeric(betelguese$magnitude)
alf_ori <- betelguese %>% select(Ymd,jd,band,magnitude) %>% filter(band=="Vis.")
summary(alf_ori)


```




### The Whole Enchilada: Jan - 1918 to Feb. 2020
```{r, echo=FALSE}
plot_ly(alf_ori) %>% add_lines(x=~Ymd,y=~magnitude) %>%
  layout(yaxis=list(autorange="reversed"))
```
```{r}
summary(alf_ori)
```


### AAVSO Zapper Simulator (Data Verificaton)

Positive observations more than 1 magnitude brighter or fainter than the mean magnitude.

Make sure you are comparing observations made using the same color filter with each other (don't try to compare a CCDB observation with a visual one, for instance). 

Also,make sure you are comparing observations made at approximately the same time (for some stars, significant changes in behavior can occur in a very short time.)

  *  Fainter-than observations that are fainter than t5>he mean curve.
  *  Observations made during the "seasonal gap" of a star.
  *  For novae and supernovae, positive observations made before outburst.


```{r,echo=FALSE}
box_plot <-alf_ori %>% filter(Ymd >="2020-01-01") 
plot_ly(box_plot) %>% add_boxplot(x = ~Ymd, y = ~magnitude) %>%
  layout(yaxis=list(autorange="reversed"))


```
```{r}
summary(box_plot)
```